Adversarial Zero-Shot Learning

### 2017-11-17 doc/paper.tex
The version submitted.

\usepackage{amsmath}	% for \begin{align}
\usepackage{graphicx}	% for \includegraphics{filename}

@@

	The architecture in Figure \ref{fig:NoisePrior} has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$. The code $\bb{h}^c$ is explicitly required to match the text representation $\bb{t}^c$ of that class, as well as regularized by the prior in the adversarial net. The learning task can be expressed as the optimization problem,
	\begin{align}
		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) + || G(\bb{x}) - \bb{t} ||_2^2 \;\right].
	\end{align}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width = 10 cm]{figNoisePrior}
\caption{Adversarial autoencoder with noise prior and explicit matching to the text representation.}
\label{fig:NoisePrior}
\end{figure}

% ---------------------------------------------------------
% ---------------------------------------------------------

\begin{figure}[!htb]
\centering
\includegraphics[width = 10 cm]{figTextPrior}
\caption{Adversarial autoencoder with text representations as positive samples drawn from some underlying prior.}
\label{fig:TextPrior}
\end{figure}

@@

	In Figure \ref{fig:TextPrior} we show the adversarial autoencoder that takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class. In this architecture, the code is driven to match the text representation through the adversarial net itself. The optimization problem for this learning scheme is of the same form of the standard adversarial autoencoder,
	\begin{align}
		\min_{G} \max_D E_{\bb{t} \sim r(\bb{t})}\left[\; \log D(\bb{t}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) \;\right],
	\end{align}
	except that the prior serves as a guide to match the text distribution rather than as a regularizer that drives the code to a Gaussian noise.

>>>>

\usepackage{amsmath}	% for \begin{align}
\usepackage{graphicx}	% for \includegraphics{filename}
\usepackage{subcaption}	% for \begin{subfigure}[t]{0.5\textwidth}

@@

	The architecture in Figure \ref{fig:Architecture} (a) has an autoencoder that learns the encoding $\bb{h}^c$ of the input images $\bb{x}^c$ belonging to a class $c$. The code $\bb{h}^c$ is explicitly required to match the text representation $\bb{t}^c$ of that class, as well as regularized by the prior in the adversarial net. The learning task can be expressed as the optimization problem,
	\begin{align}
		\min_{G} \max_D E_{\bb{z} \sim r(\bb{z})}\left[\; \log D(\bb{z}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) + || G(\bb{x}) - \bb{t} ||_2^2 \;\right].
	\end{align}

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=1.65in]{figNoisePrior}
        \caption{}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[height=1.65in]{figTextPrior}
        \caption{}
    \end{subfigure}
    \caption{Adversarial autoencoders with (a) Gaussian prior and explicit matching to the text representation, and (b) text representations as positive samples drawn from some underlying prior of text distribution.}
    \label{fig:Architecture}
\end{figure*}

@@

	In Figure \ref{fig:Architecture} (b) we show the adversarial autoencoder that takes the text representation $\bb{t}^c$ as the positive sample drawn from some underlying prior dictating the distribution of the text representation of a class. In this architecture, the code is driven to match the text representation through the adversarial net itself. The optimization problem for this learning scheme is of the same form of the standard adversarial autoencoder,
	\begin{align}
		\min_{G} \max_D E_{\bb{t} \sim r(\bb{t})}\left[\; \log D(\bb{t}) \;\right] + E_{\bb{x} \sim p_d(\bb{x})}\left[\; \log( 1 - D(G(\bb{x})) ) \;\right],
	\end{align}
	except that the prior serves as a guide to match the text distribution rather than as a regularizer that drives the code to a Gaussian noise.
